### 2023-06-16 appendix.tex
up

\section{Case: $\Bad=\downarrow \Bad$ and $\Safe=\downarrow \Safe$}\label{case down down}

We relax for now the hypothesis that $\Bad$ is the complement of $\Safe$, thus it is possible for $\Safe$ and $\Bad$ to share closure properties, i.e. for them to be both downward-closed.

% In the case \Safe and \Bad are both downward-closed, they can both be finite.

\begin{theorem}\label{down-down}
The resilience problem is undecidable for  effective WSTS with  strong  compatibility such that
%	with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\section{Case: $\Bad=\uparrow \Bad$ and $\Safe=\uparrow \Safe$.}\label{case up up}

@@

Since $\Bad \cap \Safe = \emptyset$, the subcase $\Safe = \uparrow \Safe$ and $\Bad = \uparrow \Bad$ leads to a contradiction since two upward-closed sets have not an empty intersection. We then consider the case where $\Bad$ is as upward-closed
as it can be without intersecting with $\Safe$,
i.e. 
such that there exists an upward-closed set $U$
such that $\Bad = U \setminus \Safe$.

\iffalse
\alain{à quoi ça sert ici ?: quelle signification ?Decidability of $U$ and $\Safe$ imply the decidability of $\Bad$.}
\mathieu{Pas convaincu que ça serve, je vais enlever}
% hop
\fi

example: ?

>>>>

\section{Resilience when $\Safe$ and $\Bad$ have the same closure properties}

We relax for now the hypothesis that $\Bad$ is the complement of $\Safe$, thus it is possible for $\Safe$ and $\Bad$ to share closure properties, i.e. for them to be both downward-closed or upward-closed, and we explore both possiblities.

\subsection{Case: $\Bad=\downarrow \Bad$ and $\Safe=\downarrow \Safe$}\label{case down down}

% In the case \Safe and \Bad are both downward-closed, they can both be finite.
We start with the case $\Safe = \downarrow \Safe$ and $\Bad = \downarrow \Bad$.
%
Unfortunately, in this case the resilience problem is undecidable.

\begin{theorem}\label{down-down}
The {\sc Resilience problem} is undecidable for  effective WSTS with  strong  compatibility such that
%	with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\subsection{Case: $\Bad=\uparrow \Bad$ and $\Safe=\uparrow \Safe$.}\label{case up up}

@@

We now consider the case where $\Safe = \uparrow \Safe$ and $\Bad$ is not the complement of 
$\Safe$ and we'd want $\Bad$ to have the same closure properties as $\Safe$.
We still however maintain the hypothesis that $\Bad \cap \Safe = \emptyset$, thus the subcase 
$\Safe = \uparrow \Safe$ and $\Bad = \uparrow \Bad$ leads to a contradiction, since two upward-closed sets have not an empty intersection. We thus consider instead the case where $\Bad$ is as upward-closed
as it can be without intersecting with $\Safe$,
i.e. 
such that there exists an upward-closed set $U$
such that $\Bad = U \setminus \Safe$.
